Reanalysis Step 1: Data Preparation

### 2025-08-26 reanalysis-1-data_preparation.qmd
bugfix

df_complete_original <- df_analysis |>
  filter(!is.na(CCI) & !is.na(DCSI))

@@

tibble(
  Dataset = c(
    "Full dataset (for imputation)",
    "Complete cases (original approach)", 
    "Additional observations from imputation"
  ),
  N = c(n_total, n_complete_original, n_gained_by_imputation),
  Percent = c(
    100, 
    round(n_complete_original/n_total*100, 1), 
    round(n_gained_by_imputation/n_total*100, 1)
  )
) |>
  kable(caption = "Sample size comparison: Imputation vs complete case approach")
```

@@

```{r summary}
# Final summary
tibble(
  Metric = c(
    "Total observations",
    "Complete cases (original approach)", 
    "Missing CCI or DCSI (to be imputed)",
    "Missing baseline VA (to be imputed)",
    "Patients who lapsed",
    "Patients with vision impairment"
  ),
  N = c(
    nrow(df_for_imputation),
    nrow(df_complete_original),
    sum(is.na(df_for_imputation$CCI) | is.na(df_for_imputation$DCSI)),
    sum(is.na(df_for_imputation$baseline_VA_logMAR)),
    sum(df_for_imputation$ever_lapse_binary == 1, na.rm = TRUE),
    sum(df_for_imputation$outcome_va_vi_binary == 1, na.rm = TRUE)
  )
) |>
  kable(caption = "Dataset summary for reanalysis with imputation")
```

>>>>

# Complete cases should have no missing data in key analysis variables
# This includes outcome, exposure, and all covariates
key_vars_for_complete <- c(
  "outcome_VA_logMAR",  # Outcome
  "ever_lapse_binary",   # Exposure
  "baseline_VA_logMAR",  # Key covariate
  "CCI", "DCSI",        # Comorbidity scores
  "dr_severity",         # DR severity
  "any_treatment"        # Treatment status
)

df_complete_original <- df_analysis |>
  filter(complete.cases(select(., all_of(key_vars_for_complete))))

@@

tibble(
  Dataset = c(
    "Full dataset (for imputation)",
    "Complete cases (no missing in key variables)", 
    "Additional observations from imputation"
  ),
  N = c(n_total, n_complete_original, n_gained_by_imputation),
  Percent = c(
    100, 
    round(n_complete_original/n_total*100, 1), 
    round(n_gained_by_imputation/n_total*100, 1)
  )
) |>
  kable(caption = "Sample size comparison: Imputation vs complete case approach")
```

@@

```{r summary}
# Final summary
tibble(
  Metric = c(
    "Total observations",
    "Complete cases (no missing in key variables)", 
    "Missing outcome VA (to be imputed)",
    "Missing CCI or DCSI (to be imputed)",
    "Missing baseline VA (to be imputed)",
    "Patients who lapsed",
    "Patients with vision impairment (observed)"
  ),
  N = c(
    nrow(df_for_imputation),
    nrow(df_complete_original),
    sum(is.na(df_for_imputation$outcome_VA_logMAR)),
    sum(is.na(df_for_imputation$CCI) | is.na(df_for_imputation$DCSI)),
    sum(is.na(df_for_imputation$baseline_VA_logMAR)),
    sum(df_for_imputation$ever_lapse_binary == 1, na.rm = TRUE),
    sum(df_for_imputation$outcome_va_vi_binary == 1, na.rm = TRUE)
  )
) |>
  kable(caption = "Dataset summary for reanalysis with imputation")
```
